---
title: "Basic Use"
output: 
  md_document:
    variant: markdown_github
  rmarkdown::html_vignette:
vignette: >
  %\VignetteIndexEntry{Basic_Use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


`simplebf` is a package of convenience functions for Bayes Factor analysis of two samples. The package is developed as a teaching aid for those new to Bayesian Inference and working with R. 

The functions are thin wrappers around functions in `BayesFactor` on CRAN [here](https://cran.r-project.org/package=BayesFactor) and project webpage [http://bayesfactor.blogspot.com/](http://bayesfactor.blogspot.com/). Please use that in preference. 

## Using `simplebf` for a $t$-test

To carry out Bayes Factor analysis on two named groups in a tidy dataframe use `named_pair_ttestbf()`, pass it the column names for the group and data measurements,  the name of the group to be considered as the test group, and the name of the group to be considere the control group. 

```{r setup}
library(simplebf)
result <- named_pair_ttestbf(PlantGrowth, 
                             group_col = "group", data_col = "weight",
                             control = "ctrl", test = "trt2"
                             )

```

The function returns a one row dataframe, the columns are as follows:

    1. `control_group` - the name of the group considered control
    2. `test_group` - the group considered test
    3. `h_0` - statement of the $H_0$ hypothesis
    4. `h_1` - statement of the $H_1$ hypothesis
    5. `BayesFactor` - the resulting Bayes Factor from $\frac{H_{1}/H_{0}}$
    6. `odds_h_1` - statement of the Bayes Factor in terms of odds $H_0:H_1$
    7. `summary` - summary statement of relative evidence for the hypothesis

```{r}
result %>% knitr::kable()
```

### Changing the scale of the prior and the nature $H_1$

Only one option for the `BayesFactor::ttestBF()` function can be changed. The value of `rscale` for the prior distribution can be set to one of `medium`, `wide` or `ultrawide`. The hypothesis to test as $H_1$ can be set to one of `test_greater_than_control`, `test_smaller_than_control`,`test_not_equal_to_control`.   


```{r}
result <- named_pair_ttestbf(PlantGrowth, 
                             group_col = "group", data_col = "weight",
                             control = "ctrl", test = "trt2",
                             rscale = "medium",
                             h_1 = "test_greater_than_control"
                             )
```

## Comparing all groups in a dataframe

All levels of the group column can be compared pairwise using the `allpairs_ttestbf()` function. This is called similarly to the `named_pair_ttestbf()` but without the need to specify control and test groups as all pairs are done automatically. A dataframe with the same columns as above and one row for each pair (in `A:B` _and_ `B:A` order) is returned. `rscale` and `h_1` can be used here too. 

```{r}
result <- allpairs_ttestbf(PlantGrowth, group_col = "group", data_col = "weight")
result %>% knitr::kable()
```

